Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-05 ms.tex
more

>>>>

The condition (\ref{eq:cooling2}) in conjunction with equation (\ref{eq:mdot_analytic}) also implies a maximum accretion rate for a thermally stable flow, which is given by
\begin{align}
\frac{\dot{M}_{\rm max}}{\dot{M}_{\rm edd}} \simeq
  {\rm min}\begin{cases}
   4\times 10^{-4} \eta_{0.02}^{0.47} M_{\bullet,8}^{0.34} &, \text{core}\\
   2\times 10^{-4} \eta_{0.02}^{0.59} M_{\bullet,8}^{0.29}    &, \text{cusp}\\
\eta M_{\bullet}/\dot{M}_{\rm edd}t_{\rm h} \approx 5.5\times 10^{-5}\eta_{0.02}&, v_{\rm CL} < \sigma
  \end{cases}
  \label{eq:Mdotmax}
\end{align}
